---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
source(here::here("R/model.R"))
source(here::here("R/functions.R"))
library(targets)
library(tarchetypes)
```

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above. 

```{r, eval = FALSE}
install.packages(c("dplyr", "ggplot2", "targets", "tidyr"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.



# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.


# Targets


Set the `tar_simple` chunk option to `TRUE` to define a single target with the command in the code chunk. The chunk below only contains `biglm(Ozone ~ Wind + Temp, data)` in the source, but because `tar_simple` is `TRUE`, it is shorthand for `tar_target(name = fit, command = biglm(Ozone ~ Wind + Temp, data))`. All other arguments to `tar_target()` are set to their default values (configurable with `tar_option_set()`).




# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

```{r, message = FALSE}
tar_read(report)
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.
